The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-05-08 VegOzone.tex
Updated captions and text in accordance to new plots - AOT40 plot needs to be integrated.

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[3]{Lisa}{Emberson}
\Author[2]{Aud Else}{Berglen Eriksen}
\Author[1]{Bj{\o}rg}{Rognerud}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and estimate the ozone concentration anomalies for 2018/19. In Fig.~\ref{fig:ozone_signific}, the resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month. Negative deviations from climatology are shown as negative percentage. Note that missing bars for certain months are both due to data availability (see Section~\ref{subsubsec:atmo_svanvik} for details about the time range of data taking at Svanhovd) and anomalies not meeting the criteria of $\pm 1\sigma$ deviation from climatological mean. In April/May 2018, ozone was significantly enhanced, while 2019 was generally an average year. In both years, ozone concentrations were significantly below average in November.

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_signific_1}
  \caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value (refer to Section~\ref{subsec:ozone_reco} for details) is indicated by the star. In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  \label{fig:ozone_signific}
\end{figure}

>>>>

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\Author[3]{Lisa}{Emberson}
\Author[3]{Connie}{O'Neill}
\Author[2]{Aud Else}{Berglen Eriksen}
\Author[1]{Bj{\o}rg}{Rognerud}
\Author[1]{Frode}{Stordal}
\Author[1]{Terje}{Koren Berntsen}

@@

In accordance to the above findings, we adjust the derived ozone climatology for Svanvik by adding a constant bias correction factor $\Delta\chem{[O_3]_\mathrm{bias-corr}} = 1.2\,\unit{ppb}$ and estimate the ozone concentration anomalies for 2018/19. In Fig.~\ref{fig:ozone_signific}, the resulting percentage of days above/below $\pm 1\,\sigma$ from the bias-corrected climatological mean is displayed for each month. Negative deviations from climatology are shown as negative percentage. Note that missing bars for certain months are both due to data availability (see Section~\ref{subsubsec:atmo_svanvik} for details about the time range of data taking at Svanhovd) and anomalies not meeting the criteria of $\pm 1\sigma$ deviation from climatological mean. In April/May 2018, ozone was significantly enhanced, while 2019 was generally an average year. In both years, ozone concentrations were significantly below average in November. July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is, however, indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details of the used method for gap filling).

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_signific_1}
  \caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details). In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  \label{fig:ozone_signific}
\end{figure}
